\documentclass{cta-author}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage[export]{adjustbox}

\newtheorem{theorem}{Theorem}{}
\newtheorem{corollary}{Corollary}{}
\newtheorem{remark}{Remark}{}

\begin{document}

	% New definitions
  \algnewcommand\algorithmicswitch{\textbf{switch}}ep
  \algnewcommand\algorithmiccase{\textbf{case}}
  \algnewcommand\algorithmicassert{\texttt{assert}}
  \algnewcommand\Assert[1]{\State \algorithmicassert(#1)}%
  % New "environments"
  \algdef{SE}[SWITCH]{Switch}{EndSwitch}[1]{\algorithmicswitch\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicswitch}%
  \algdef{SE}[CASE]{Case}{EndCase}[1]{\algorithmiccase\ #1}{\algorithmicend\ \algorithmiccase}%
  \algtext*{EndSwitch}%
  \algtext*{EndCase}%

\supertitle{Submission Template for IET Research Journal Papers}

\title{I am still here}

\author{\au{First Author$^{1}$}, \au{Second Author$^{2\corr}$}, \au{Third Author$^{3}$}}

\address{\add{1}{First Department, First University, Address, City, Country Name}
\add{2}{Second Company Department, Company Address, City, Country Name}
\add{3}{Third Department, Third University, Address, Country Name}
\add{4}{Current affiliation: Fourth Department, Fourth University, Address, Country Name}
\email{corresponding.author@second.com}}

\begin{abstract}
This should be informative and suitable for direct
inclusion in abstracting services as a self-contained
article. It should not exceed 200 words. It should
summarise the general scope and also state the main results
obtained, methods used, the value of the work and the
conclusions drawn. No figure numbers, table numbers,
references or displayed mathematical expressions should be
included. The abstract should be included in both the
Manuscript Central submission step (Step 1) and the
submitted paper.
\end{abstract}

\maketitle

\input{SIN-body}

\section*{Example References}\label{sec13}

\subsection{Websites}\label{subsec13.1}

\begin{enumerate}
\item[{[1]}] `Author Guide - IET Research Journals',
http://digital-library.theiet.org/journals/author-guide, accessed 27
November 2014\vspace*{6pt}

\item[{[2]}] `Research journal length policy',
http://digital-library.theiet.org/ files/research\_journals\_length\_policy.pdf,
accessed 27 November 2014
\end{enumerate}

\subsection{Patent}\label{subsec13.2}

\begin{enumerate}
\item[{[3]}] `ORCID: Connecting research and researchers', http://orcid.org/,
accessed 3 December 2014\vspace*{6pt}

\item[{[4]}]
`Fundref', http://www.crossref.org/fundref/, accessed 4 December 2014
\end{enumerate}

\subsection{Journal articles}\label{subsec13.3}

\begin{enumerate}
\item[{[5]}] Smith, T., Jones, M.: 'The title of the paper', IET Syst. Biol., 2007,
1, (2), pp. 1--7\vspace*{6pt}

\item[{[6]}] Borwn, L., Thomas, H., James, C.,~et al.:'The title of the paper, IET
Communications, 2012, 6, (5), pp 125-138
\end{enumerate}

\subsection{Conference Paper}\label{subsec13.4}

\begin{enumerate}
\item[{[7]}]
Jones, L., Brown, D.: 'The title of the conference paper'. Proc. Int.
Conf. Systems Biology, Stockholm, Sweden, May 2006, pp. 1--7
\end{enumerate}

\subsection{Book, book chapter and manual}\label{subsec13.5}

\begin{enumerate}
\item[{[8]}] Hodges, A., Smith, N.: 'The title of the book chapter', in Brown, S.
(Ed.): 'Handbook of Systems Biology' (IEE Press, 2004, 1st edn.), pp. 1--7\vspace*{6pt}

\item[{[9]}]
Harrison, E.A., and Abbott, C.: 'The title of the book' (XYZ Press,
2005, 2nd edn. 2006)
\end{enumerate}

\subsection{Report}\label{subsec13.6}

\begin{enumerate}
\item[{[10]}] IET., 'Report Title' (Publisher, 2013), pp. 1-5\vspace*{6pt}

\item[{[11]}] Brown, F.: 'The title of the patent (if available)'. British Patent
123456, July\vadjust{\pagebreak} 2004

\item[{[12]}] Smith, D., Hodges, J.: British Patent Application 98765, 1925
\end{enumerate}

\subsection{Thesis}\label{subsec13.7}

\begin{enumerate}
\item[{[13]}]
Abbott, N.L.: 'The title of the thesis'. PhD thesis, XYZ University,
2005
\end{enumerate}

\subsection{Standard}\label{subsec13.8}

\begin{enumerate}
\item[{[14]}] BS1234: 'The title of the standard', 2006
\end{enumerate}

\begin{table}[!h]
\fwprocesstable{Example of large table\label{tab2}}
{\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}\toprule
Column heading 1 &Column heading 2 & Column heading 3  & Column heading 4\\
\midrule
Result 1 &123 &123 & 123 \\
Result 2 &123 &123 &123 \\
Result 3 &123 &123 &123 \\
Result 4 &123 &123 &123 \\
Result 5 &123 &123 &123 \\
Result 6 &123 &123 &123 \\
Result 7 &123 &123 &123 \\
Result 8 &123 &123 &123 \\
\botrule
\end{tabular*}}{}
\end{table}

\vfill\pagebreak

\section{Appendices}\label{sec14}

Additional material, e.g. mathematical derivations, tables and figures
larger than half a page that may interrupt the flow of your paper's argument
should form a separate Appendix section (see Table~\ref{tab2}). Do not, however, use
appendices to lengthen your article unnecessarily as this section is
included in the word count. If the material can be found in another work,
cite this work rather than reproduce~it.
The appendix section should be in double column format, and come after the references.

\end{document}
