\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage[export]{adjustbox}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[SIN'18]{Security of Information and Networks}{September 2018}{Cardiff University, Cardiff}
\acmYear{2018}
% \copyrightyear{2016}


% \acmArticle{4}
% \acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
% \editor{Jennifer B. Sartor}
% \editor{Theo D'Hondt}
% \editor{Wolfgang De Meuter}


\begin{document}

  % New definitions
  \algnewcommand\algorithmicswitch{\textbf{switch}}
  \algnewcommand\algorithmiccase{\textbf{case}}
  \algnewcommand\algorithmicassert{\texttt{assert}}
  \algnewcommand\Assert[1]{\State \algorithmicassert(#1)}%
  % New "environments"
  \algdef{SE}[SWITCH]{Switch}{EndSwitch}[1]{\algorithmicswitch\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicswitch}%
  \algdef{SE}[CASE]{Case}{EndCase}[1]{\algorithmiccase\ #1}{\algorithmicend\ \algorithmiccase}%
  \algtext*{EndSwitch}%
  \algtext*{EndCase}%

\title{A Fine-grained Access Control Technique to Protect Sensitive Healthcare Data in Emergency Cases with Dynamic Security Policies}

\author{Luong Khiem Tran}
\affiliation{%
  \institution{University of Technology}
  \city{Ho Chi Minh}
  \country{Vietnam}
}
\email{7140242@hcmut.edu.vn}

\author{Ha Xuan Son}
\affiliation{%
  \institution{University of Technology}
  \city{Ho Chi Minh}
  \country{Vietnam}
}
\email{hxson@ctuet.edu.vn}

\author{Tran Khanh Dang}
\affiliation{%
  \institution{University of Technology}
  \city{Ho Chi Minh}
  \country{Vietnam}
}
\email{khanh@hcmut.edu.vn}

\author{Kim Tuyen Le}
\affiliation{%
  \institution{University of Technology}
  \city{Ho Chi Minh}
  \country{Vietnam}
}
\email{tuyenltk@hcmut.edu.vn}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{L.K. Tran et al.}

\begin{abstract}
One primary requirement for the healthcare industry is prioritizing the provision of information to support the patient's health. 
For this reason, access control mechanisms for health systems to regulate and limit disclosure of data are often ignored in the event of an emergency. 
This phenomenon, called "Break The Glass" is a popular model for healthcare systems, but from a security point of view it represents a serious weakness. 
In fact, malicious users can take advantage of this principle to gain unauthorized access and privileges. 
There are a number of solutions offered in previous research, but these approaches still contain %quite a lot of limitations. 
some limitations.
These restrictions have not been a complete replacement for the BTG principle yet in an emergency situation. 
In addition, it is so difficult that previous approaches can be applied to the actual situation as the main barrier comes from the complexity and the flexibility of the healthcare system. 
%In this paper, we propose an access control solution, aiming to better regulate exceptions while ensuring data availability. 
%This paper will propose an access control solution, aiming to better regulate exceptions while ensuring data availability. 
This paper propose Model of Access Control for HealthCare system (ACDP-HC Model), aiming to better regulate exceptions while ensuring data availability. 
Our solution is based on allowing for a flexible mix of policies created by admin and patient. 
Besides, the mechanism supporting dynamic policy also adds the flexibility to the ACDP-HC. 
In the evaluation, we compared ACDP-HC Model with previous approaches. 
As a result, ACDP-HC better supports than that. 
We also have developed a proof-of-concept for this mechanism and we show some experimental results based on difference % dynamic policy scenarios.
scenarios.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10003006.10011608</concept_id>
<concept_desc>Security and privacy~Information flow control</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Information flow control}

\keywords{access control, healthcare system, break the glass, dynamic policy, rewriting request, policy evaluation}

\maketitle

\input{SIN-body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibfile}

\end{document}
